Online Appendix

### 2021-04-16 src/online_appendix.Rmd
online appendix to add text

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE, fig.height=10}
#out.width='100%'

@@

# not used
# for.tip.mean.up.pm <- TS2020 %>% # raw data, individual tests
#   filter(hour(date)==19 | hour(date)==20) %>% 
#   group_by(LAD19NM) %>%
#   summarise(mean.up.pm = mean(speedup)) 
# 
# for.tip.mean.up <- TS2020 %>% # raw data, individual tests
#   group_by(LAD19NM) %>%
#   summarise(mean.up = mean(speedup)) 
# 
# # download metrics
# for.tip.mean.down.am <- TS2020 %>% # raw data, individual tests
#   filter(hour(date)==9 | hour(date)==10) %>% 
#   group_by(LAD19NM) %>%
#   summarise(mean.down.am = mean(speeddown)) 
# 
# for.tip.mean.up.pm <- TS2020 %>% # raw data, individual tests
#   filter(hour(date)==19 | hour(date)==20) %>% 
#   group_by(LAD19NM) %>%
#   summarise(mean.down.pm = mean(speeddown)) 
# 
# for.tip.mean.up <- TS2020 %>% # raw data, individual tests
#   group_by(LAD19NM) %>%
#   summarise(mean.down = mean(speeddown))

@@

# create the text to tooltip
la.f <- merge(la.f, for.tip.mean.up.am, by.x = "id", by.y = "LAD19NM", all.x=T)
#sapply(la.f, function(x) sum(is.na(x)))
#No am data points for Isles of Scilly
la.f$tip <- paste0(la.f$id, "<br>",
                   "Upload AM speed: ", round(la.f$mean.up.am), " Kbps", "<br>",
                   "Rank: ", la.f$rank)
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

@@

### LAD mean AM upload speeds and ranking

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE,fig.height=10}
for.tip.mean.up.am <- merge(for.tip.mean.up.am, clusters.nodiff, 
                            by.x = "LAD19NM", by.y = "LAD", all.x = T)

for.tip.mean.up.am %>% 
  select(-cluster.down, -cluster.tests) %>% 
  arrange(rank) %>% 
  kable(digits = 0,
        format.args = list(big.mark = ","),
        col.names = c("Local Authority",
                      "Mean AM upload sped",
                      "Rank",
                      "Cluster")) %>% 
  kable_styling("striped", full_width = F) %>% 
  scroll_box() #width = "500px", height = "400px"
```

@@

>>>>

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE, fig.height=10, fig.asp=T}
#out.width='100%'

@@

for.tip.mean.up.pm <- TS2020 %>% # raw data, individual tests
  filter(hour(date)==19 | hour(date)==20) %>%
  group_by(LAD19NM) %>%
  summarise(mean.up.pm = mean(speedup))

# not used
# for.tip.mean.up <- TS2020 %>% # raw data, individual tests
#   group_by(LAD19NM) %>%
#   summarise(mean.up = mean(speedup)) 
# 
# # download metrics
# for.tip.mean.down.am <- TS2020 %>% # raw data, individual tests
#   filter(hour(date)==9 | hour(date)==10) %>% 
#   group_by(LAD19NM) %>%
#   summarise(mean.down.am = mean(speeddown)) 
# 
# for.tip.mean.up.pm <- TS2020 %>% # raw data, individual tests
#   filter(hour(date)==19 | hour(date)==20) %>% 
#   group_by(LAD19NM) %>%
#   summarise(mean.down.pm = mean(speeddown)) 
# 
# for.tip.mean.up <- TS2020 %>% # raw data, individual tests
#   group_by(LAD19NM) %>%
#   summarise(mean.down = mean(speeddown))

@@

# create the text to tooltip
la.f <- merge(la.f, for.tip.mean.up.am, by.x = "id", by.y = "LAD19NM", all.x=T)
la.f <- merge(la.f, for.tip.mean.up.pm, by.x = "id", by.y = "LAD19NM", all.x=T)

#sapply(la.f, function(x) sum(is.na(x)))
#No am data points for Isles of Scilly
la.f$tip <- paste0(la.f$id, "<br>",
                   "Mean upload AM speed: ", round(la.f$mean.up.am), " Kbps", "<br>",
                   "Mean upload PM speed: ", round(la.f$mean.up.pm), " Kbps")
la.f <- la.f[order(la.f$order),] # if i don't order merge.nuts.f loses order and the map has gaps

@@

### LAD mean AM and PM upload speeds

```{r, echo=FALSE, warning=FALSE, message = FALSE, error=FALSE,fig.height=10}
for.tip.mean.up.am <- merge(for.tip.mean.up.am, clusters.nodiff, 
                            by.x = "LAD19NM", by.y = "LAD", all.x = T)
for.tip.mean.up.am <- merge(for.tip.mean.up.am, for.tip.mean.up.pm, 
                            by.x = "LAD19NM", all.x = T)

for.tip.mean.up.am %>% 
  select(-cluster.down, -cluster.tests, -rank) %>% 
  arrange(-mean.up.am) %>% 
  relocate(cluster.up, .after=mean.up.pm) %>% 
  kable(digits = 0,
        format.args = list(big.mark = ","),
        col.names = c("LAD",
                      "Mean AM upload speed",
                      "Mean PM upload speed",
                      "Cluster")) %>% 
  kable_styling("striped", full_width = F) %>% 
  scroll_box() #width = "500px", height = "400px"
```

@@

- Cluster 3:

- Cluster 4:

- Cluster 5:

- Cluster 6:
